%LATEX Header
\documentclass[11pt, twocolumn]{article}
\usepackage[letterpaper]{geometry}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}
\usepackage{times}
\usepackage{amssymb,amsmath}

% Title Page
\title{CUDA Implementation of Jacobi Relaxation}
\author{Neeraja Budamagunta, Torben Rasmussen, Sweta Sharma, John Wehland, Matthew Wolfe}
\date{7/20/2011}

\begin{document}
\maketitle
\section{Abstract}
\section{Introduction} %background/context, the idea, summary of results
The graphics processing unit (GPU) is an application-specific device aimed at rapidly building images for viewing on a display.
Over the past decade, GPUs have become more and more general purpose, and can now be called general purpose GPUs (GP-GPUs).
Software frameworks such as CUDA and OpenCL have allowed researchers to tap into the parallelism that exists in these devices.
These frameworks allow the creation of parallel mathematical applications that can be deployed on low-cost, readily available hardware.
CUDA, or Compute Unified Device Architecture, is Nvidia's parallel computing architecture.
This architecture gives a programmer access to the underlying hardware through a few layers of abstraction, allowing for relatively high-level programming.
A GPU can offer a very high computational rate if the algorithm is well-suited for the device.
One such application is matrix computation.
Matrix applications like the Jacobi relaxation work well in parallel.
As such, it is well suited to work with on GP-GPU’s.

The rest of our report is organized in the following way.
The next section talks about our project idea, design and analysis of solution to our problem.
Section 3 shows the actual implementations followed by the results achieved.
In section 4 we discuss work related to ours and finally conclude in section 5.
We had limited goals due to shortage of time and resources, so we discuss future work in section 6.

    \subsection{Background} %CUDA, math

\section{Our Project}
    \subsection{Requirements} %hardware, software
    \subsection{Analysis} %how do we do testing, what are we measuring, etc.
    \subsection{Design} %what we did, how did we improve it (performance tuning).  input matrix size, kernel code (including block size), etc.

\section{Results} %prove the idea is good
Till now we have talked about the algorithm and design of our problem. In this section we show the
actual implementation and the results we got using these optimizations. We actually worked on two
levels of optimizations on [reference], one of those is the one kernel optimizations and the other one is
maximizing the throughput according to the array size.
    \subsection{Implementation 1: One Kernel Optimization}
    Our first optimization is to implement Jacobi relaxation in CUDA with one kernel. In [reference]
    Michael has implemented Jacobi relaxation in CUDA using two kernel calls per iteration. Instead as an
    optimization we use a single kernel call per iteration reducing the over head to initiate an extra kernel
    each time. The reason for using two kernels initially was to reduce the change values across the blocks
    to one single value. These change values were reduced from one change value per thread to a change
    value per block, in the first kernel 'jacobikernel'. In the second kernel with fewer numbers of threads
    and one single block those values are reduced to one single change value. In our implementation we
    used the existing threads to do the additional work of further reducing the per block change values to
    a single value. With this optimization we were able to reduce the calculation time to 10%. However we
    could not reduce it much further because though here we are reducing the over head of initialization of
    a new kernel and creating new threads, but in our implementation there are other threads in the end
    which sit idle and do not have much work to do. However this is a possible way of optimization which
    did give us positive results. In the table below we have shown a few array sizes, their performance with

    one kernel (our implementation), performance with two kernels (as in [reference]) and the performance
    improvement of one kernel, over two kernel implementation.

    \begin{center}
        \begin{tabular}{ | p{1.3cm} | p{1.5cm} | p{1.5cm} | p{1.6cm} | p{1.6cm} | p{2cm} | p{1.9cm} | p{2cm} | }
            \hline
            Array Size  & One kernel total time (s) & Two kernel total time (s) & One kernel calc. time (s) & Two kernel calc. time (s) & Improvement on total time (s) & Improvement on calc. time (s) & Improvement in calc. time: 1 kernel over 2 kernel (\%) \\ \hline
            130x130 & 0.108135    & 0.106293    & 0.009158    & 0.010240    & 0.98296574  & 1.11814807  & 10.5  \\
            146x146 & 0.104811    & 0.106242    & 0.010526    & 0.011699    & 1.01365315  & 1.11143834  & 10    \\
            162x162 & 0.131627    & 0.115655    & 0.014078    & 0.015089    & 0.87865711  & 1.07181418  & 6.7   \\
            178x178 & 0.115519    & 0.118052    & 0.018908    & 0.020070    & 1.02192713  & 1.06145547  & 5.7   \\
            194x194 & 0.119967    & 0.119893    & 0.021031    & 0.022331    & 0.99938316  & 1.06181351  & 5.8   \\
            210x210 & 0.125773    & 0.128649    & 0.024906    & 0.026340    & 1.02286659  & 1.05757649  & 5.4   \\
            226x226 & 0.128909    & 0.130154    & 0.029529    & 0.030782    & 1.00965798  & 1.04243286  & 4     \\
            242x242 & 0.137315    & 0.150276    & 0.034656    & 0.037037    & 1.09438881  & 1.06870383  & 6.4   \\
            \hline
        \end{tabular}
    \end{center}

    \subsection{implementation 2}
    \subsection{summary} % of results with graphs/tables/etc.

\section{Related Work} %prove the idea is new? It really isn't, but it's our take on existing software.  This section may be small.
    \subsection{michael wolfe!!}
    \subsection{mention} %other papers we read in class?

\section{Conclusion} %repeat idea, summarize key results

\section{Future Work} %list the things you wanted to do but couldn't finish in time for this paper
\section{Acknowledgements} %mention wolfe et al
\end{document}
